Reviews

### 2018-09-05 revision/reviews.tex
coverage rate script and more comments to the reviewers

\answerfin{The reviewer is concerned that more attention needs to be given concerning issues in boundary cases with the coverage rates.  Although the given explanation seems to have switched $\alpha$ and $1-\alpha$ in a few places the point is helpful and clear especially with the generously provided examples included for the finite population case.  We have reproduced similar results using simulation in the infinite population 2-phase context and have concluded that this indeed occurs with the sampling fraction between the first and second phases is less than $\alpha$.  For this reason we have expanded the confidence interval section to inform the reader of this situation.}
\\

@@

Also section 5 on CIs could be considerably shortened. Needs to be a section on its own right? Sections 6 and 7 are very interesting but the R code under 7.1 could probably be condensed a lot.\\
\\
\answerfin{Reviewer 1 made a very valid criticism about designed-based confidence intervals when the sampling fraction is too small that we would like to include in the paper and Section 5 is the most logical place to put it.} \\

@@

@@

@@

\answerfin{In this context "a biased estimate" is an estimate that is produced from a biased estimator.  It would be a bit tedious to explain every time that an given estimate was produced from a biased estimator.}
% --------------------------- %

@@

@@

@@

\answerfin{It is elegant in the sense that the SAE estimator is unbiased merely by modifying the design matrix.  It is not necessary to refit every small area with an indicator, but it is  how the package implemented the estimator.}
% --------------------------- %

% XX) ++++++++++++++++++++++++++ %
\item \textit{After eq. 14. How can there be a residual correction term in a synthetic estimator? There may not even be observations available from within small area G. Please describe and define the term $\theta_s2$ in more detail.}.

\answerfin{It says that "the formulas look similar to the synthetic estimators", because they are exactly same.  They merely have a modified design matrix.}
% --------------------------- %

@@

>>>>

\answerfin{The reviewer is concerned that more attention needs to be given concerning issues in boundary cases with the coverage rates.  The given explanation seems to have switched $\alpha$ and $1-\alpha$ in a few places.  Regardless the concept of having a sampling fraction too low for the confidence level isn't really applicable in the infinite population approach where the total population of points is infinity.  We have performed simulations under the infinite population approach and could not reproduce this point.  However, the reviewer does have a valid point that discussing coverage rates would improve the paper. For this reason we have expanded the confidence interval section to include some simulated examples of coverage rates to develop the reader's intuition about when the sample size is too low to produce reliable results.}
\\

@@

Also section 5 on CIs could be considerably shortened. Needs to be a section on its own right? Sections 6 and 7 are very interesting but the R code under 7.1 could probably be condensed a lot.\\
\\
\answerfin{Reader 1 suggested that this section in fact be extended to include discussion about coverage rates.  We prefer to go in this direction.} \\

@@

\answerfin{$n_2G < 6$ is just a rule of thumb.  In Section 2.4, the goal was merely to introduce the small area problem in a general sense for readers that were not familiar.  Rules of thumb should not be blindly obeyed though so we thought it best to refer to it when examples are present to give context allow the reader to develop intuition.  Further discussion of this rule of thumb including simulation examples are included in the confidence interval section in the context of coverage rates.}
% --------------------------- %

@@

\answerfin{This is usually the case, but the estimators are both random and the opposite may sometimes occur.  They are asymptotically equivalent though.  The point is that one should prefer the g-weight because it attempts to account for sampling variation in the coefficients whereas the external variance completely ignores it.  This is explained on page 11 after the example for the global two-phase estimator.}
% --------------------------- %

@@

\answerfin{Unbiased point estimates are point estimates produced by unbiased point estimators.}
% --------------------------- %

@@

\answerfin{The extended synthetic estimator does not necessarily need to implement an ancova model.  That depends on the types of variables that the user has specified.  The extended synthetic estimator merely adds an indicator variable for the small area in addition to the other variables that the user specified.}
% --------------------------- %

@@

\answerfin{The reviewers comments refer to the version of the package that is already available on CRAN and has over 5000 downloads.  We prefer not to alter the function parameters in order to preserve backwards compatibility.}
% --------------------------- %

@@

\answerfin{It is elegant in the sense that the estimator is unbiased merely by modifying the design matrix.  It is not necessary to refit every small area with an indicator, but this is it was implemented in the package.}
% --------------------------- %

% XX) ++++++++++++++++++++++++++ %
\item \textit{After eq. 14. How can there be a residual correction term in a synthetic estimator? There may not even be observations available from within small area G. Please describe and define the term $\theta_{s_2}$ in more detail.}.

\answerfin{It says that "the formulas look similar to the synthetic estimators", because the formulas are exactly same.  They merely have a modified design matrix that ensures that the residual correction term is zero by construction and doesn't need to be included.   $\theta_{s_2}$ is now clearly defined in Eq. 13 and the preceeding paragraph.}
% --------------------------- %

@@

\answerfin{The reviewer's comment refers to the help documentation of the R-package.  The twophase() function can be used to estimate in both the global and small area contexts.  $Z_bar_1G$ refers to the small area context whereas $Z_bar_1$ is the terminology used for global estimation (i.e. when G = F).  In the future release of the package we will try to include a short reference to this distinction in the help documentation but given that the package already has over 5000 downloads we prefer not to change the names of the function outputs.}
% --------------------------- %
